### 2020-02-10 README.Rmd
Support Warp LDA and correct all typos of 'WrapLDA'. fix #3

`newsgroup_stm` is an example topic model trained with the data `newsgroup5` using the `stm` package. Currently, this package supports structural topic models / correlated topic models from `stm` and Wrap LDA models from `text2vec`.

@@

@@

>>>>

`newsgroup_stm` is an example topic model trained with the data `newsgroup5` using the `stm` package. Currently, this package supports structural topic models / correlated topic models from `stm` and Warp LDA models from `text2vec`.

@@

## About Warp LDA

There is a subtle difference between the support for `stm` and for `text2vec`.

`newsgroup_warplda` is a Warp LDA object trained with the same dataset as the `newsgroup_stm`

```{r warplda}
newsgroup_warplda
```

All the API endpoints are the same, except the one for the creation of topic intrusion test cases. You must supply also the `input_dfm`.

```{r warplda2}
### Just word intrusion test.
oolong_test <- create_oolong(newsgroup_warplda)
oolong_test
```

```{r warplda3}
newsgroup5_dfm
```

```{r warplda4}
oolong_test <- create_oolong(newsgroup_warplda, newsgroup5$text, input_dfm = newsgroup5_dfm)
oolong_test
```

@@

---
